---
title: "temperature_sandbox"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This markdown is used to explore home temperatures in 4 rooms, collected by Govee sensors.

Import data:

```{r}
library(tidyverse)
library(fs) # file system
library(lubridate) # date
library(tidyr) # long to wide data transformation
library(prophet) # fb's forecast package
library(forecast) # time series forecast

data_dir <- "/Users/apple/Dropbox/temperature/data/201908"

csv_files <- fs::dir_ls(data_dir, regexp = "\\.csv$")

data <- csv_files %>% map_dfr(read_csv, .id = "source")
```

Data summary:

```{r}
summary(data)
```

Filter out August data and seperate rooms:
```{r}
aug_data <- data %>%
  filter(`Timestamp for sample frequency every 1 min` >= "2019-08-01 00:00:00" 
         & `Timestamp for sample frequency every 1 min` <= "2019-08-31 23:59:59" ) %>%
  mutate(room = case_when(grepl("1bedroom", source)          ~ "1bedroom", 
                          grepl("2nd Floor Bedroom", source) ~ "2bedroom",
                          grepl("2office", source)           ~ "2office",
                          grepl("kitchen", source)           ~ "kitchen")) %>%
  select(-source) %>%
  rename(time = `Timestamp for sample frequency every 1 min`)
```

Plot temperature for different rooms:

```{r}
aug_data %>%
  ggplot(aes(x = time
             , y = Temperature_Fahrenheit
             , color = room)) +
  geom_line()
```

Plot humidity for different rooms:

```{r}
aug_data %>%
  ggplot(aes(x = time
             , y = Relative_Humidity
             , color = room)) +
  geom_line()
```
Basic statistics by room:
```{r}
aug_data %>%
  group_by(room) %>%
  summarise(mean_temp = mean(Temperature_Fahrenheit)
            , max_temp  = max(Temperature_Fahrenheit)
            , min_temp  = min(Temperature_Fahrenheit)
            , sd_temp   = sd(Temperature_Fahrenheit)
            , mean_humidity = mean(Relative_Humidity)
            , max_humidity  = max(Relative_Humidity)
            , min_humidity  = min(Relative_Humidity)
            , sd_humidity   = sd(Relative_Humidity))
```

Change data from long to wide form:

```{r}
aug_data %>%
  pivot_wider(id_cols = time
              , names_from = room
              , values_from = c(Temperature_Fahrenheit, Relative_Humidity)) -> aug_data
```


Correlation between temperature and humidity:

```{r}
cor.test(aug_data[, 2, drop = TRUE], aug_data[, 6, drop = TRUE])$estimate
cor.test(aug_data[, 3, drop = TRUE], aug_data[, 7, drop = TRUE])$estimate
cor.test(aug_data[, 4, drop = TRUE], aug_data[, 8, drop = TRUE])$estimate
cor.test(aug_data[, 5, drop = TRUE], aug_data[, 9, drop = TRUE])$estimate
```

Interestingly, the correlation coef is different across rooms.

Correlation qmong temperatures in different rooms:

```{r}
cor.test(aug_data[, 2, drop = TRUE], aug_data[, 3, drop = TRUE])$estimate # 1b with 2b
cor.test(aug_data[, 2, drop = TRUE], aug_data[, 4, drop = TRUE])$estimate # 1b with 2o
cor.test(aug_data[, 2, drop = TRUE], aug_data[, 5, drop = TRUE])$estimate # 1b with k
cor.test(aug_data[, 3, drop = TRUE], aug_data[, 4, drop = TRUE])$estimate # 2b with 2o
cor.test(aug_data[, 3, drop = TRUE], aug_data[, 5, drop = TRUE])$estimate # 2b with k
cor.test(aug_data[, 4, drop = TRUE], aug_data[, 5, drop = TRUE])$estimate # 2o with k
```


Sort data with date:

```{r}
aug_data <- arrange(aug_data, time)
```


